|

### 2021-09-28 03-Chp-Systematic-Review.Rmd
End of day:

<!-- -   TODO Look at whether searching preprints made any difference to my results -->

@@

Following full-text screening, 87 reports describing 78 unique studies met the criteria for inclusion in the review.[@ancelin2012a; @ancelin2013; @andrews2019a; @arvanitakis2008; @batty2014; @benn2017b; @bettermann2012a; @beydoun2011; @bruce2017; @burgess2017; @chao2015a; @chen2014; @chiang2007; @chitnis2015; @chou2014a; @chuang2015; @cramer2008; @dodge2011; @forti2010; @gnjidic2016; @gottesman2017; @gustafson2012; @haag2009; @hayden2006; @heartprotectionstudycollaborativegroup2002; @hendrie2015; @hippisley-cox2010a; @jick2000; @kimm2011; @kivipelto2001; @kivipelto2005a; @kuo2015; @li2004; @li2005a; @li2010; @liao2013; @liu2019a; @mainousa.g.2005; @mielke2005a; @mielke2010a; @mielke2011; @mukherjee2013; @muller2007; @noale2013; @notkola1998; @ostergaard2017; @pan2018; @parikh2011; @peters2009; @raffaitin2009; @rantanen2017; @rea2005a; @redelmeier2019; @reitz2004a; @reitz2010; @ridker2008; @ronnemaa2011; @schilling2017a; @smeeth2009a; @so2017; @solomon2007; @solomon2009a; @solomon2010; @sparks2008; @strand2013; @svensson2019; @szwast2007; @tan2003a; @tynkkynen2016; @tynkkynen2018; @wang2012; @whitmer2005a; @yang2015; @yoshitake1995; @zamrini2004; @zandi2005; @zhu2018a; @zimetbaum1992] Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.

@@

@@

<!----------------------------------------------------------------------------->
(ref:preprintGrowth-cap) __Growth of preprint repositories over time__ - Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv n= `r n_at_search["bio"]`, medRxiv n = `r n_at_search["med"]`), the relative number of hits returned by each is expected.

>>>>

@@

```{r characteristicsSetup, message=FALSE, results="asis", echo = FALSE}
```

Following full-text screening, 87 reports describing `r n_included` unique studies met the criteria for inclusion in the review.[@ancelin2012a; @ancelin2013; @andrews2019a; @arvanitakis2008; @batty2014; @benn2017b; @bettermann2012a; @beydoun2011; @bruce2017; @burgess2017; @chao2015a; @chen2014; @chiang2007; @chitnis2015; @chou2014a; @chuang2015; @cramer2008; @dodge2011; @forti2010; @gnjidic2016; @gottesman2017; @gustafson2012; @haag2009; @hayden2006; @heartprotectionstudycollaborativegroup2002; @hendrie2015; @hippisley-cox2010a; @jick2000; @kimm2011; @kivipelto2001; @kivipelto2005a; @kuo2015; @li2004; @li2005a; @li2010; @liao2013; @liu2019a; @mainousa.g.2005; @mielke2005a; @mielke2010a; @mielke2011; @mukherjee2013; @muller2007; @noale2013; @notkola1998; @ostergaard2017; @pan2018; @parikh2011; @peters2009; @raffaitin2009; @rantanen2017; @rea2005a; @redelmeier2019; @reitz2004a; @reitz2010; @ridker2008; @ronnemaa2011; @schilling2017a; @smeeth2009a; @so2017; @solomon2007; @solomon2009a; @solomon2010; @sparks2008; @strand2013; @svensson2019; @szwast2007; @tan2003a; @tynkkynen2016; @tynkkynen2018; @wang2012; @whitmer2005a; @yang2015; @yoshitake1995; @zamrini2004; @zandi2005; @zhu2018a; @zimetbaum1992] Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.

@@

of interest, many of the included studies were peformed in Taiwan (`r n_taiwan`), all but one of which made use of the Taiwan National Health Insurance.

@@

<!----------------------------------------------------------------------------->
(ref:preprintGrowth-cap) __Growth of preprint repositories over time__ - Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv n= `r n_at_search["bio"]`, medRxiv n = `r n_at_search["med"]`), the number of hits returned by each is expected.

### 2021-09-28 05-Chp-IPD-Analysis.Rmd
Back to a working version
End of day:

@@

@@

@@

As part of the IPD analysis, relevant cohort studies were identified from the sty and approached. In the first instance, the corresponding author on the main man

Talk about how different covariates were managed across cohorts, 
c
<!-- TODO Read this[@riley2020] -->

@@

### Data sources

Several cohort studies were approach

<!-- Need exact number approach -->

As part of this Chapter, I will use individual patient data from a range of sources. These sources are described here in detail for reference.

These data source

Each should have:

* Description (including observation period, numbers, numbers with outcome, etc)
*

@@

#### CaPS

The CPRD is introduced more fully in . Briefly, a similar approach to the cohort definition as used in Chapter

#### EPIC Norfolk

#### Generation Scotland

#### NICOLA

#### TRACK HD

@@

included in previous IPD meta-analysis (Endnote ID: 2140)

Different approaches to combining subgroups. [@fisher2017]

@@

@@

#### BRACE

@@

#### Memento
Excluded as criteria for entry was outpatients from memory clinic (unlikely to be dementia free at baseline)

#### Generation Scotland

@@

#### NICOLA

@@

#### ELSA

@@

@@

Maybe discuss here t

This was particularly frustrating in the case of cohorts which had a dedicated data access panel, for example, the Three City Study. Despite multiple attempts to contact the team, there was no response received.

@@

### Data cleaning

Across all cohorts, data cleaning was performed in a similary manner, using commonly named variables, so that a single model could be applied using functional programming.

@@

Talk about missing data was handled <!-- IDEA See Sean's thesis for some additional detail on this -->

<!--- Inlcude CPRD analysis here, but dou --->

<!-- TODO talk about different methods - see here: https://onlinelibrary.wiley.com/doi/10.1002/sim.8516 -->

All analysis were standardised by changes in 1-SD of the exposure variable.

This was done to aid interpretability of the outcome.

A two-stage model was used out of necessity, with the one-stage model being recluded by the different datasets being in protected data silos.

<!-- TODO Figure showing the outline of interval censored studies. -->

Data

@@

<!-- TODO text -->

@@

While this is not unexpected, given that a review of IPD studies published between 1987 and 2015 found that fewer than half managed to obtained data from greater than 80% of studies, and that in many cases, the exact percentage of studies for which data was obtained was not accurately reported.
test
There are likely several reasons for this.

@@

&nbsp;
<!----------------------------------------------------------------------------->

### Reflections on data access

@@

Even with the guaranteed data access afforded by the DPUK, accessing sufficient data was

@@

Previous SWARs have

>>>>

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
source("R/helper.R")
knitr::read_chunk("R/05-Code-IPD-Analysis.R")
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
```

@@

As part of a broader investigation into the relationship between lipid levels and dementia risk, I sought to

@@

### Applying for data access

__Systematic review__

@@

As part of the IPD analysis, relevant cohort studies identified through the systematic review detailed in Chapters \@ref(sys-rev-heading) were. In the first instance, the corresponding author on the main man

__Dementia platform UK__

In addition, to assess the results for  the Dementia Platform UK common-access procedure was utilised. In short, this approach is intended to make it easier to access data from exisiting dementia cohorts through a centralised application process.

Talk about how different covariates were managed across cohorts,

### Eligibility criteria

Lipids reported/available as a continuous measure, and were not cross-sectional.

Due to the limited time-frame, studies making use of population-level electronic health records, which often require an entire project proposal, were ineligible due to the time and cost involved in applying. The one exception to this was data from the CPRD, which we already had access to via the study reported in Chapter \'ref(cprd-heading).

<!-- TODO Read this[@riley2020] -->

Talk about missing data were handled <!-- IDEA See Sean's thesis for some additional detail on this -->

@@

<!-- Be clear on the different types of databases, e.g. those where users are followed up regularly vs those where participants are captured via EHR-->

&nbsp;<!----------------------------------------------------------------------->

&nbsp;<!----------------------------------------------------------------------->

<!-- TODO talk about different methods - see here: https://onlinelibrary.wiley.com/doi/10.1002/sim.8516 -->
<!-- TODO Figure showing the outline of interval censored studies. -->

All analysis were standardised by changes in 1-SD of the exposure variable. This was done to aid interpretability of the outcome.

A two-stage model was used out of necessity, with the one-stage model being precluded by the different datasets being in protected data silos.

In order to investigate the interaction of patient-level characteristics with lipid levels, interaction terms for lipid-covariate terms were included in the model above. These were extracted and synthesised using a random effects meta-analysis.

Where results were comparably to previously published estimates, these were compared and reasons for any discrepancies discussed.

The analysis were carried out in R (Version...) using the following packages: `survival`[@survival-book], `metafor`[@viechtbauer2010a]

__Replicating published findings__

Where any included data source had previously been analysed and results for the association between lipid levels and dementia reported, these were compared to the results of this analysis.

&nbsp;<!----------------------------------------------------------------------->

### Data access

<!-- Need exact number from each approach, plus detailed exclusion reasons -->

Of the XXX studies to which I applied for data access, only three were eventually included in the analysis. Figure \@ref(fig:cohortFlowchart) details whether the cohorts eventually included in the review were identified by the systematic review or via DPUK portal.

In addition, the reasons for cohorts not being included in the analysis are presented. In summary, the requests for data from cohorts identified by the systematic review was characterised by a very low response rate. For the minority who did respond, common reasons given by corresponding authors for not sharing the data included that they no longer worked in the lab, had access to the data, or that they were currently or intended to perform a similar analysis as the one proposed.

For the streamlined DPUK process, where a dedicated project manager liases with cohort owners, the overall response rate was higher, result in access to three cohorts. However, even using th

<!----------------------------------------------------------------------------->
```{r cohortFlowchartSetup, include = FALSE}
```

(ref:cohortFlowchart-cap) Flowchart of included cohorts, stratified by identification method (systematic review vs DPUK).

(ref:cohortFlowchart-scap) Flowchart

```{r cohortFlowchart, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cohortFlowchart-cap)', out.width='100%', fig.scap='(ref:cohortFlowchart-scap)'}
knitr::include_graphics(file.path("figures/ipd/cohortFlowchart.png"))
```
<!----------------------------------------------------------------------------->

Few cohorts were included in both the DPUK and the systematic review sets of cohorts indicating that the DPUK.

I did not request data from several DPUK cohorts due to the information on the online system indicating that the study was relatively new (and so was yet to collect >1 wave of data, as in the case of the XXXX cohort) or the online data dictionary indicating that the exposure variables of interest were not recorded.

As highlighted in the

### Included data sources

The three datasets included are described in detail in the following section, and are summarised in Table \@ref(tab:cohortOverview-table).

Of note, all data sources included in the analysis were based in the United Kingdom. This is likely due to the majority of included datasets coming from the Dementia Platform UK route \@ref(fig:cohortFlowchart), which as implied by the name, has a geographical focus on studies performed in Great Britain United Kingdom.

&nbsp;

<!----------------------------------------------------------------------------->
(ref:cohortOverview-caption) Summary of cohorts for which data were available

(ref:cohortOverview-scaption) Summary of included cohorts

```{r cohortOverview-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

&nbsp;

<!-- TODO Update table with SD for age, and check why number of events in EPIC is less than expected (5 vs 8)-->

<!-- TODO * Description (including observation period, numbers, numbers with outcome, etc) -->

&nbsp;<!----------------------------------------------------------------------->

#### Caerphilly Prospective Study

The Caerphilly <!-- TODO Check spelling --> Prospective Study is a longitudinal study of men in the

Cholesterol measures (total, LDL-c, HDL-c and triglycerides) were measured at baseline in 1979-1983. 
As the study population has aged, additional outomes. Of particular relevance to this analysis, from Phase III (1989-1993) onwards, a battery of congnitive tests were introduced.

&nbsp;<!----------------------------------------------------------------------->

The CPRD is introduced more fully in Chapter \@ref(). Briefly, a similar approach to the cohort definition as used in Chapter

&nbsp;<!----------------------------------------------------------------------->

@@

&nbsp;<!----------------------------------------------------------------------->

@@

This data source was analysed in one of the included studies identified by the systematic review presented in Chapter \@ref(sys-rev-heading).[@tynkkynen2018]

This gave

&nbsp;<!----------------------------------------------------------------------->

@@

As highlighted in Figure \@ref(fig:cohortFlowchart), several cohorts from the DPUK responding positively but on inspection of data provided these cohorts were excluded.

@@

The reasons for exclusion of these cohorts for which data were provided is illustrated in Table \@ref(tab:dataExcluded-table).

__BRACE__

@@

__Memento__

Excluded as criteria for entry was outpatients from memory clinic (unlikely to be dementia free at baseline)

__Generation Scotland__

@@

__NICOLA__

@@

__ELSA__

@@

&nbsp;

<!----------------------------------------------------------------------------->
(ref:dataExcluded-caption) dataExcluded

(ref:dataExcluded-scaption) dataExcluded

```{r dataExcluded-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

&nbsp;

@@

A particularly frustrating in the case of cohorts which had a dedicated data access panel, for example, the Three City Study. Despite multiple attempts to contact the team, there was no response received.

@@

### Data cleaning and harmonisation

Across all cohorts, data cleaning was performed in a similar manner, using commonly named variables, so that a single model could be applied using functional programming.

@@

@@

@@

While this is not unexpected, given that a review of IPD studies published between 1987 and 2015 found that fewer than half managed to obtained data from greater than 80% of studies, and that in many cases, the exact percentage of studies for which data were obtained was not accurately reported.
test
There are likely several reasons for this.

@@

For the purposes of this thesis, conducting the IPD was useful as it afforded me the opportunity to experience the methodology.

On a personal level, given the

In addition, it allowed me to analysed two addition previously unanalysed cohort studies which were then utilised in the triangulation study detailed in Chapter \@ref(tri-heading).

&nbsp;<!----------------------------------------------------------------------->

### Resources

While it was disappointing that such a small proportion of the available data were obtained for analysis, in terms of project completion, it is probably a good thing.

Given the resource intensity of data cleaning and harmonisation,

&nbsp;<!----------------------------------------------------------------------->

### Data access

Couple of sections

* Problems with getting data from studies
*

Sharing data has several legal, ethical and logistical challenges, and can often

This is in theory what the DPUK was built to address. However, despite claims to a streamlined process, the response rate amond cohorts participating

@@

Even with the guaranteed data access afforded by the DPUK, accessing sufficient data were

Of the XXX cohorts requested from the DPUK, allowing for a year lag since application, a response was received from only XXX (XXX%), while of those responding a minority

@@

Options could include

Previous SWARs have been registered as protocols, but have not yet reported!

&nbsp;<!----------------------------------------------------------------------->

### Reflections on the process

May have been overly ambitious
